### 2018-07-23 README.Rmd
remove hyperlink for a sometimes bad url

	<td style="text-align:left;"><a href="http://www.indexfungorum.org/ixfwebservice/fungus.asmx">link</a></td>

>>>>

	<!-- <td style="text-align:left;"><a href="http://www.indexfungorum.org/ixfwebservice/fungus.asmx">link</a></td> -->
	<td style="text-align:left;"><p>http://www.indexfungorum.org/ixfwebservice/fungus.asmx</p></td>
